A user-extensible and adaptable parser architecture

### 2008-05-30 doc/logparser.tex
Better looking output from \refwithpage{} command.
Misc notes and minor changes.
Lots of corrections after proofreading.
Converted normal-vs-smaller graph to show the increase in execution time rather     than the decrease. Wrote about number of rules scalability. Wrapped labels on some graphs so they don't extend past the edge of the graph.

% Useful stuff for math mode.
\usepackage{amstext}
% Wrapping of URLs; this doesn't work in the bibliography, but the breakurl
% package does.
%\usepackage{url}
% The name of the program, so I only have to change it in one place.
\newcommand{\parsername}{\PLP{}}
\newcommand{\parsernames}{\PLP{}'s}
% Include images
\usepackage[final]{graphicx}
% Change how nested enumerate environments are labelled.
\renewcommand{\labelenumii}{\roman{enumii}:}
\renewcommand{\refname}{Bibliography}
% Add the bibliography into the table of contents.
\usepackage[section,numbib]{tocbibind}
% Provides commands to distinguish between pdf and dvi output.
\usepackage{ifpdf}

\usepackage[acronym=true,style=altlist,number=none,toc=true]{glossary}
\makeglossary{}
\makeacronym{}

@@

@@

\newcommand{\numberOFrules}[0]{%
    165%
}

@@

>>>>

% Useful stuff for math mode.
\usepackage{amstext}
% The name of the program, so I only have to change it in one place.
\newcommand{\parsername}{\PLP{}}
\newcommand{\parsernames}{\PLP{}'s}
% Include images
\usepackage[final]{graphicx}
% Change how nested enumerate environments are labelled.
\renewcommand{\labelenumii}{\roman{enumii}:}
\renewcommand{\refname}{Bibliography}
% Add the bibliography into the table of contents.
\usepackage[section,numbib]{tocbibind}
% Provides commands to distinguish between pdf and dvi output.
\usepackage{ifpdf}

% global=true prevents acronyms being expanded twice
\usepackage[global=true,acronym=true,style=altlist,number=none,toc=true]{glossary}
\makeglossary{}
\makeacronym{}

@@

% Sort numbers where there are multiple citations.  Doesn't appear to have
% any effect, though it does reduce the space between numbers.
\usepackage{cite}

@@

\newcommand{\numberOFrules}[0]{%
    169%
}

@@

XXX IS THERE A SYMBOL FOR APPENDIX, LIKE \textsection{} FOR SECTIONS\@?

XXX CHECK Y-AXIS LABELS ON GRAPHS TO ENSURE THEY CAN BE READ, AND WRAP IF
NECESSARY\@.

### 2008-05-30 papers/sgai-2008/paper.tex
Converted normal-vs-smaller graph to show the increase in execution time rather     than the decrease. Wrote about number of rules scalability. Wrapped labels on some graphs so they don't extend past the edge of the graph.

@@

\subsection{Architecture Scalability}

@@

>>>>

\newcommand{\numberOFrulesMINIMUM}[0]{%
    119 XXX CHECK THIS NUMBER%
}

% \numberOFrulesMINIMUM as percentage of \numberOFrules
\newcommand{\numberOFrulesMINIMUMpercentage}[0]{%
    70.41\%%
}

% \numberOFrules as percentage increase of \numberOFrulesMINIMUM
\newcommand{\numberOFrulesMAXIMUMpercentage}[0]{%
    42.01\%%
}

@@

\subsection{Architecture Scalability: Input size}

@@

\subsection{Architecture Scalability: Number of Rules}

How any architecture scales as the number of rules increases is important,
but it is particularly important in this architecture because it is
expected that there will be a large number of rules.  There are
\numberOFrules{} rules in the full ruleset, whereas the minimum number of
rules required to parse the \numberOFlogFILES{} log files is
\numberOFrulesMINIMUM{}, \numberOFrulesMINIMUMpercentage{} of the total.  A
second set of statistics was generated using the minimum ruleset and the
results compared to the statistics generated using the full ruleset: the
percentage execution increase when using the full ruleset instead of the
minimal ruleset for normal, shuffled and reversed orderings is shown in
fig.~\refwithpage{Percentage execution time increase of maximum ruleset
over minimum ruleset}.  \showgraph{build/plot-normal-vs-smaller}{Percentage
execution time increase of maximum ruleset over minimum ruleset}{Percentage
execution time increase of maximum ruleset over minimum ruleset}

It is clear from fig.~\refwithpage{Percentage execution time increase of
maximum ruleset over minimum ruleset} that the increased number of rules
makes a noticeable difference with the reverse ordering, and to a lesser
extent with the shuffled ordering.  The normal ordering (where rules are
sorted so that the most frequently matching rules are tried first) shows a
\input{build/normal-vs-smaller-percentage-increase.tex} increase in
execution time for a \numberOFrulesMAXIMUMpercentage{} increase in the
number of rules.  These results show that the architecture scales very well
as the number of rules increases, and that sorting the rules is an
important optimisation enabling the parser to scale well.
